

\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[scale=0.75]{geometry}
\usepackage{emoji}

% personal data
\name{Umut}{Seven}
\title{Curriculum Vit\ae}                               % optional, remove / comment the line if not wanted
\address{Bristol, UK}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+44~(736)~682~3919}                   % optional, remove / comment the line if not wanted
\email{umutseven92@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{umutseven.com} 


\begin{document}

\makecvtitle

\section{Summary}
\vspace{5px}

Over 5 years of experience as a Full Stack Software Engineer with a focus on APIs and microservices.\newline{}
M.S. in Software Engineering from Boğaziçi University.\newline{}
Currently working as a Lead Engineer at Cookpad.\newline{}

\vspace{5px}


\begin{itemize}
\item Languages: Python, Rust, Dart, C\#, Java, Javascript, SQL, HTML, CSS, F\#, C, Prolog
\item Frameworks: Django, Flask, FastAPI, Flutter, Svelte, .NET, Spring
\item Cloud: AWS, GCP, Firebase
\item DevOps: Docker, Kubernetes, Terraform
\item Other: Elasticsearch (ELK), Lucene, Kafka
\end{itemize}

\section{Professional Experience}

\cventry{Jun 2021 -- Currently Employed}{Lead Engineer}{Cookpad}{Bristol, UK}{Python, FastAPI, Kafka, Kubernetes, Terraform}{Led the engineering team for the Search Team. Constant collaboration with Product Managers. Led development of new features. \newline{}} 

\cventry{Jan 2021 -- Jun 2021}{Search Engineer}{Cookpad}{Bristol, UK}{Python, FastAPI, Kafka, Kubernetes, Terraform}{Developed the search system for Cookpad, including Elasticsearch \& API services. Tuned relevance. \newline{}} 

\cventry{Mar 2019 -- Jan 2021}{Full Stack Engineer}{Cookpad}{Bristol, UK}{Flutter, Dart, Python, Django, Svelte}{Developed both Android and iOS apps using Flutter \& Dart, website via Svelte, API via Django , Firebase tools like Cloud Firestore, Firebase Cloud Messaging and Firebase Cloud Functions. \newline{}} 

\vspace{5px}

\cventry{Sep 2018-- Feb 2019}{Software Developer}{4play Digital Workshop}{Istanbul, Turkey}{Java, Spring, RabbitMQ}{Development of web services and miscellaneous VAS services for mobile operators. Designing the software development process and implementing agile methodologies for the development team. \newline{}} 
\vspace{5px}

\cventry{Feb 2018-- Aug 2018}{Software Developer}{Armut}{Istanbul, Turkey}{C\#, .NET, Javascript}{Development of both the front-end and the back-end services of armut.com, leveraging multiple AWS products to deploy and monitor services. Implementing the CI/CD pipeline of multiple microservices. \newline{}} 
\vspace{5px}

\cventry{Sep 2015--Feb 2018}{Software Developer}{P.I. Works}{Istanbul, Turkey}{C\#, .NET, JavaScript}{Development of multiple real-time software projects that optimize \& profile base stations, making the mobile operators more efficient and less error prone. Design and development of customized DevOps tools. \newline{}} 
\vspace{5px}

\cventry{Jul 2014--Sep 2014}{Software Development Intern}{P.I. Works}{Istanbul, Turkey}{C\#, .NET, JavaScript, Python}{Development of web \& desktop based performance monitoring and reporting tools. Improving the CI/CD process. \newline{}} 
\vspace{5px}

\section{Education}
\vspace{5px}

\cventry{2017--2019}{Software Engineering}{Boğaziçi University}{Istanbul, Turkey}{\textit{MS}}{}  % arguments 3 to 6 can be left empty
\vspace{5px}
\cventry{2010--2015}{Business Administration}{Istanbul University}{Istanbul, Turkey}{\textit{BBA}}{}  % arguments 3 to 6 can be left empty
\vspace{5px}

\section{Personal Projects}
\vspace{5px}
\cventry{}{Python}{LaFontaine}{}{}{
LaFontaine is an automatic movie trailer generator. LaFontaine creates movie trailers for any genre using pre-defined features, like number of faces on screen, and loudness of volume. Scenes are extracted using these features and combined to create the final trailer. There are three features for frame, three features for sound and three features for subtitles. Features are read from configurations and are fully configurable.
 \newline{}%
Links:%
\begin{itemize}%
\item \url{https://github.com/umutseven92/LaFontaine}\newline{}
\end{itemize}}

\vspace{5px}
\cventry{}{Python, Django}{Sentweet}{}{}{
Sentweet is a sentiment analyzer \& visualizer that uses the Twitter API. It allows users to perform sentiment analysis via a web user interface. It queries the Twitter API and charts out the general feelings people have about a certain topic. This project was built for Boğaziçi University Software Engineering Masters Programme, under the supervision of Prof. Dr. Suzan Üsküdarli. \newline{}%
Links:%
\begin{itemize}%
\item \url{https://github.com/umutseven92/Sentweet}\newline{}
\end{itemize}}
\vspace{5px}

\cventry{}{C\#, ASP.NET Core}{Plutus}{}{}{Plutus is a customizable, exchange agnostic cryptocurrency trading bot. You configure which cryptocurrencies to buy \& sell, your desired profit amount \& loss tolerance, and which cryptocurrency exchanges you want to buy \& sell from. It does the rest by predicting if the price is going up or down for a given coin and buying and selling according to your profit and loss stops. \newline{}%
Links:%
\begin{itemize}%
\item \url{https://github.com/umutseven92/Plutus}\newline{}
\end{itemize}}
\vspace{5px}
\cventry{}{C\#, .NET Core}{SharpChain}{}{}{SharpChain is a simple blockchain implementation for educational purposes, written in C\#. It is a simpler, smaller model of the Bitcoin blockchain. I believe it makes it easier to see how the blockchain actually works nicely. \newline{}%
Links:%
\begin{itemize}%
\item \url{https://github.com/umutseven92/SharpChain}\newline{}
\end{itemize}}
\vspace{5px}
\color{color3}

\vspace{5px}


\section{Certifications \& Training}
\vspace{5px}

\textbf{Qualifications}
\begin{itemize}
\item Microsoft Certified Professional (MC ID: 10495811)
\item TÜBİTAK 2014 Software Competition Finalist\newline{}
\end{itemize}
\textbf{Certificates}
\begin{itemize}
\item Microsoft Certified Professional Certificate (E498-2569)
\item Programming in C\# Specialist Certificate (E498-2567)
\item Bilge Adam MCSD Certificate of Excellence
\item Bilge Adam MCSD Participation\newline{}
\end{itemize}

\textbf{Training}
\begin{itemize}
\item MCSD Training in Bilge Adam\newline{}
\end{itemize}

\vspace{5px}


\section{Miscellaneous}
\vspace{5px}

\cvitemwithcomment{Hobbies}{Musician (\emoji{guitar}, \emoji{musical-keyboard}, \emoji{drum})}{}
\cvitemwithcomment{Other}{Fluent in English (IELTS Score of 8.5)}{}

               
\vspace*{\fill}
\color{color2} \centerline{\{ The source code for this CV can be found at https://github.com/umutseven92/UmutSevenCV \}}
\end{document}
