

\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[scale=0.75]{geometry}
\usepackage{emoji}
\usepackage{fontawesome5}

% personal data
\name{Umut}{Seven}
\title{Curriculum Vit\ae}                               % optional, remove / comment the line if not wanted
\address{Bristol, UK}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+44~(736)~682~3919}                   % optional, remove / comment the line if not wanted
\email{umutseven92@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{https://umutseven.com}
\github{umutseven92}

\begin{document}

\makecvtitle

\section{Summary}

Seasoned Full Stack Software Engineer with a decade of expertise in API and Microservice development. I deliver reliable and scalable solutions, covering everything from intuitive web and mobile experiences to complex backend infrastructure designed to serve millions of users. I've thrived in diverse environments, from large corporations to early-stage startups.
\\In short, I'm an engineer; I solve problems.
\\\\M.S. in Software Engineering, Boğaziçi University.
\\


\begin{itemize}
\item Languages: Python, Rust, Dart, C\#, Java, JavaScript, SQL, HTML, CSS, F\#, C, Prolog
\item Frameworks: Django, Flask, FastAPI, Flutter, Svelte, .NET, Spring
\item Cloud: AWS, GCP, Firebase
\item DevOps: Docker, Kubernetes, Terraform
\item Other: Elasticsearch, Lucene, Kafka
\end{itemize}

\section{Professional Experience}

\cventry{Jul 2024 -- Present}{Senior Software Engineer}{Sunbeam (\href{https://www.sunbeam.cx/}{sunbeam.cx})}{Bristol, UK}{Python, FastAPI, Next.js, Tailwind, Terraform}{
\lambda \ Spearheaded the development of Sunbeam's core product as a founding engineer, developing its complete technical stack including infrastructure, back-end, front-end, and an AI-driven feedback analytics pipeline. \\
\lambda \ Created and optimised applications to process high-volume ChatGPT requests, enabling quick insight generation from a high volume of feedback. \\
\lambda \ Designed and implemented comprehensive monitoring and logging services to ensure system reliability and performance.}{AWS}

\cventry{Jun 2021 -- Jul 2024}{Lead Engineer}{Cookpad (\href{https://cookpad.com/uk}{cookpad.com})}{Bristol, UK}{Python, FastAPI, Elasticsearch, Kafka, Kubernetes, Terraform}{
\lambda \ Led development of critical new features, managed technical debt initiatives, and streamlined the software development lifecycle for the Core Search Team, collaborating closely with Product Managers. Maintained existing contributions as a Search Engineer. \\
\lambda \ Guided a diverse team of over 10 engineers, fostering an environment that ensured the delivery of a highly effective and intuitive search experience for all users.}{AWS}

\cventry{Jan 2021 -- Jun 2021}{Search Engineer}{Cookpad}{Bristol, UK}{Python, FastAPI, Elasticsearch, Kafka, Kubernetes, Terraform}{
\lambda \ Developed and optimised core search systems for Cookpad, encompassing APIs, ETL pipelines, and Elasticsearch-based services. \\
\lambda \ Significantly improved search quality through strategic relevance tuning, in close collaboration with Product and Country Managers. \\
\lambda \ Built foundational search infrastructure, leveraging technologies like Terraform and Kubernetes. \\
\lambda \ Partnered with Machine Learning Engineers to seamlessly integrate ML-driven solutions into Cookpad's search ecosystem.}{AWS}

\cventry{Mar 2019 -- Jan 2021}{Full Stack Engineer}{Cookpad}{Bristol, UK}{Flutter, Dart, Python, Django, Svelte, JavaScript, HTML, CSS}{
\lambda \ As the sole developer on a greenfield skunkworks project, designed and built a complete product ecosystem, including: cross-platform mobile apps (Android/iOS) with Flutter \& Dart, a customer-facing web app using Svelte, a REST API with Django, and all underlying infrastructure powered by Firebase (Cloud Firestore, Cloud Messaging, Cloud Functions). \\
\lambda \ Operated within a lean, agile team, driving rapid prototyping and iterative development through numerous design sprints (à la The Sprint Book).}{Firebase, GCP}

\cventry{Sep 2018-- Feb 2019}{Software Developer}{4play Digital Workshop (\href{https://www.4play.com.tr/}{4play.com.tr})}{Istanbul, Turkey}{Java, Spring, RabbitMQ}{
\lambda \ Developed and deployed web services and various Value-Added Services (VAS) tailored for mobile operators.  \\
\lambda \ Designed and implemented agile software development methodologies, significantly improving the development team's efficiency and responsiveness.}{}

\cventry{Feb 2018-- Aug 2018}{Software Developer}{Armut (\href{https://armut.com/}{armut.com})}{Istanbul, Turkey}{C\#, .NET, JavaScript, HTML, CSS} {
\lambda \ Engineered the full stack for \href{https://www.armut.com}{\underline{armut.com}}, developing both front-end and back-end services and utilising multiple AWS products for seamless deployment and robust monitoring. \\
\lambda \ Implemented comprehensive CI/CD pipelines across multiple microservices, streamlining development workflows.
}{AWS}

\cventry{Sep 2015--Feb 2018}{Software Developer}{P.I. Works (\href{https://piworks.net/}{piworks.net})}{Istanbul, Turkey}{C\#, .NET, JavaScript, HTML, CSS}{
\lambda \ Engineered multiple real-time software projects to optimize and profile mobile base stations, significantly enhancing mobile operator efficiency and reducing errors.  \\
\lambda \ Designed and developed customised DevOps tools, streamlining workflows for the engineering team
}{}

\cventry{Jul 2014--Sep 2014}{Software Development Intern}{P.I. Works}{Istanbul, Turkey}{C\#, .NET, JavaScript, Python}{
\lambda \ Engineered comprehensive web and desktop-based tools for performance monitoring and reporting. \\
\lambda \ Optimised the CI/CD process, enhancing efficiency and accelerating software delivery.}{}

\section{Education}

\educationentry{2017--2019}{Software Engineering}{Boğaziçi University}{Istanbul, Turkey}{MS}{
Papers:
\begin{itemize}
    \item{\href{https://drive.google.com/file/d/10RAU24_aWX4O_XMQ8Altn1MbYMl6gjFG/view?usp=sharing}{\underline{Survey of Android Malware Detection}}}
    \item{\href{https://drive.google.com/file/d/1AANtE8J-ZnvdytCmMGu-Yn2ohU0c5VWR/view?usp=sharing}{\underline{Survey of Software Bug Prediction}}}
    \item{\href{https://drive.google.com/file/d/1dr5dlokARmxddnZ7p35_pzb-XdSPXWk3/view?usp=sharing}{\underline{TCP Vegas: End to End Congestion Avoidance on a Global Internet}}}
    \item{\href{https://drive.google.com/file/d/1hNLGdiBpXnLHhV1JelKjq3fkIAPxW0FU/view?usp=sharing}{\underline{Automatic Trailer Generation for Movies}}}
\end{itemize}} 

\educationentry{2010--2015}{Business Administration}{Istanbul University}{Istanbul, Turkey}{BBA}{}
\section{Selected Personal Projects}

\projectentry{apyr}{Python, FastAPI}{apyr (all lowercase) is a simple \& easy to use mock API server. Great for front-end development when your API is not ready, or when you are prototyping an API- also very useful for demos \& hackathon!}{https://github.com/umutseven92/apyr}

\projectentry{LaFontaine}{Python, NLTK}{
LaFontaine is an automatic movie trailer generator. LaFontaine creates movie trailers for any genre using pre-defined features, like number of faces on screen, and loudness of volume. Scenes are extracted using these features and combined to create the final trailer. There are three features for frame, three features for sound and three features for subtitles. Features are read from configurations and are fully configurable.}
{https://github.com/umutseven92/LaFontaine}

\projectentry{Shorts Blocker}{CSS, Chrome Extension}{
Shorts Blocker is a simple Chrome extension that blocks YouTube shorts, using CSS injection. Also available in the \href{https://chromewebstore.google.com/detail/shorts-blocker/ckagfhpboagdopichicnebandlofghbc}{\underline{Chrome Web Store}.}}
{https://github.com/umutseven92/shorts-blocker}

\projectentry{Godspeed}{Lua, Playdate}{Godspeed is a simple game for Playdate, inspired by the movie Speed. You play as a bus, speeding down a highway full of obstacles, and if you slow down, or crash too much, the bomb explodes. Also available on \href{https://umutseven92.itch.io/godspeed}{\underline{itch.io}.}}
{https://github.com/umutseven92/godspeed}

\vspace{20px}


\color{color2} \centerline{\{ This isn't all! See more at \href{https://github.com/umutseven92}{github.com/umutseven92}. \}}

\color{color3}


\vspace{5px}

\pagebreak

\section{Certifications \& Training}

\textbf{Qualifications}
\begin{itemize}
\item Microsoft Certified Professional (MC ID: 10495811)
\end{itemize}

\vspace{5pt}

\textbf{Certificates}
\begin{itemize}
\item Microsoft Certified Professional Certificate (E498-2569)
\item Programming in C\# Specialist Certificate (E498-2567)
\end{itemize}

\vspace{5pt}

\textbf{Training}
\begin{itemize}
\item \href{https://badgr.com/public/assertions/m5HJzTYOSBKl15TJ0P3vQw}{\underline{Think Like A Relevance Engineer - Elasticsearch by OpenSource Connections}}
\end{itemize}

\vspace{5pt}


\section{Miscellaneous}


\cvitemwithcomment{Hobbies}{Making music, playing Go ($\sim$16 kyu), Screenwriting}{}
\cvitemwithcomment{Other}{Fluent in English (IELTS Score of 8.5, both Academic and General)}{}

               
\vspace*{\fill}
\color{color2} \centerline{\{ This CV is also on GitHub! Check it out at \href{https://github.com/umutseven92/CV}{github.com/umutseven92/CV}. \}}

\color{color3}

\end{document}
